Computationally Efficient Simulation of Queues: The \proglang{R} Package \pkg{queuecomputer}

### 2020-07-18 paper.tex
Include chapter 4 Usage Update software versions

\Address{
  Anthony Ebert\\
  School of Mathematical Sciences\\
  Science and Engineering Faculty\\
  Queensland University of Technology\\
  Brisbane Queensland 4000, Australia\\
  E-mail: \email{ac.ebert@qut.edu.au}\\
  URL: \url{https://acems.org.au/our-people/anthony-ebert}
}

@@

The simulation was conducted on a system with Intel (R) Core(TM) i7-6700 CPU @ 3.40GHz running Debian GNU/Linux. The version of \proglang{R} is 3.5.1 ``Feather spray'' with \pkg{simmer} version 4.0.1 and \pkg{queuecomputer} version 0.8.3. The version of \proglang{Python} is 3.5.3 with \pkg{simpy} module version 3.0.11.

>>>>

\Address{
  Anthony Ebert\\
  School of Mathematical Sciences\\
  Science and Engineering Faculty\\
  Queensland University of Technology\\
  Brisbane Queensland 4000, Australia\\
  E-mail: \email{anthonyebert@gmail.com}\\
  URL: \url{https://anthonyebert.github.io/resume/}
}

@@

The simulation was conducted on a system with Intel (R) Core(TM) i7-6700 CPU @ 3.40GHz running Debian GNU/Linux. The version of \proglang{R} is 4.0.2 ``Taking Off Again'' with \pkg{simmer} version 4.4.2 and \pkg{queuecomputer} version 0.9.1. The version of \proglang{Python} is 3.8.2 with \pkg{simpy} module version 4.0.1.
